Co-moving stars in \textsl{Gaia DR1}

### 2016-11-16 paper/ms.tex
fixed CCA affiliation, added to Hogg. fixed #21
Modify color magnitude diagrams
- Fix y-axis label
- Output to rasterized pdf

\title{Co-moving stars in \textsl{Gaia DR1}}
\author{Semyeong Oh\altaffilmark{\pu,\lead},
        Adrian M. Price-Whelan\altaffilmark{\pu},
        David W. Hogg\altaffilmark{\ccpp,\mpia},
        Timothy D. Morton\altaffilmark{\pu},
        David N. Spergel\altaffilmark{\pu,\cca}
}

@@

\altaffiltext{\pu}{Department of Astrophysical Sciences,
                   Princeton University, Princeton, NJ 08544, USA}
\altaffiltext{\lead}{To whom correspondence should be addressed:
                     \texttt{semyeong@astro.princeton.edu}}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
                     Department of Physics,
                     New York University, 4 Washington Place,
                     New York, NY 10003, USA}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                     K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cca}{Simons Center for Computational Astrophysics, ...,
                    New York, NY XXXXX, USA}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/gjg_graphviz_examples.png}
  \end{center}
  \caption{
    Color-magnitude diagrams of stars in larger networks presented in
    Figure~\ref{fig:graphviz_examples}. Each panel shows the same network
    visualized in the panel at the same position
    in Figure~\ref{fig:graphviz_examples}.
    We show the distribution of all stars common in \tgas\ and \tmass\
    with parallax $S/N>16$ in blue for reference.
    \label{fig:cmd_large}}
\end{figure*}

>>>>

\title{Co-moving stars in \textsl{Gaia DR1}}
\author{Semyeong Oh\altaffilmark{\pu,\lead},
        Adrian M. Price-Whelan\altaffilmark{\pu},
        David W. Hogg\altaffilmark{\ccpp,\mpia,\cca},
        Timothy D. Morton\altaffilmark{\pu},
        David N. Spergel\altaffilmark{\pu,\cca}
}

@@

\altaffiltext{\pu}{Department of Astrophysical Sciences,
                   Princeton University, Princeton, NJ 08544, USA}
\altaffiltext{\lead}{To whom correspondence should be addressed:
                     \texttt{semyeong@astro.princeton.edu}}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
                     Department of Physics,
                     New York University, 4 Washington Place,
                     New York, NY 10003, USA}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                     K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cca}{Center for Computational Astrophysics, 162 5th Ave, New York, NY 10003, USA}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{figures/gjg_graphviz_examples.pdf}
  \end{center}
  \caption{
    Color-magnitude diagrams of stars in larger networks presented in
    Figure~\ref{fig:graphviz_examples}. Each panel shows the same network
    visualized in the panel at the same position
    in Figure~\ref{fig:graphviz_examples}.
    We show the distribution of all stars common in \tgas\ and \tmass\
    with parallax $S/N>16$ in blue for reference.
    \label{fig:cmd_large}}
\end{figure*}
